Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-06 WSSSPE3/report/wg_main_funding_spec_expert.tex
remove extra space

Having convinced ourselves that this would be a positive innovation, we were
then faced with the specific question of how to fund the initiation of this
activity. A self-sustaining research software group will support itself through
collaborations with PIs in the normal grant process, with PIs choosing to fund
some amount of research software engineering effort through grants in the usual
way. However, to bootstrap such a function to a level where it has sufficient
reputation and client base to be self -sustaining will generally require seed
investment.

>>>>

Having convinced ourselves that this would be a positive innovation, we were
then faced with the specific question of how to fund the initiation of this
activity. A self-sustaining research software group will support itself through
collaborations with PIs in the normal grant process, with PIs choosing to fund
some amount of research software engineering effort through grants in the usual
way. However, to bootstrap such a function to a level where it has sufficient
reputation and client base to be self-sustaining will generally require seed
investment.
